\documentclass{article}

\usepackage[margin=1.5cm, includefoot, footskip=30pt]{geometry}
\usepackage[parfill]{parskip}
\usepackage[black]{merriweather} %% Option 'black' gives heavier bold face 
\usepackage[T1]{fontenc}
\usepackage{hyperref}
\usepackage{minted}

\pagenumbering{gobble}

\title{Computing for Mathematics: Handout 1}
\date{}

\begin{document}

\maketitle


This handout contains a summary of the topics covered as well as outline of
expected progress.

For further practice you can do the exercises available at 
\href{https://vknight.org/pfm/building-tools/01-variables-conditionals-loops/exercises/main.html}{the
Variables, conditionals and loops chapter of Python for Mathematics}.

\section{Expected progress}
\hrule

At the end of this week you should have a group assigned.

\begin{itemize}
    \item Agree on a way for your group to stay in touch;
    \item Schedule 1 or 2 regular meeting times a week to work specifically on
        the project.
    \item Have an exchange of early ideas of possible project topics.
\end{itemize}

\begin{center}
\framebox{
\textbf{At this stage I would expect you to have some ideas written down.}
}
\end{center}

\section{Summary}\label{summary}
\hrule

The programming topics covered in the
\href{https://vknight.org/pfm/building-tools/01-variables-conditionals-loops/introduction/main.html}{variables,
conditionals and loops chapter of Python for Mathematics} are:

\begin{itemize}
\item
  Creating variables

        \begin{minted}[frame=single]{python}
age = 40
        \end{minted}
\item
  Run code depending on a given condition.


        \begin{minted}[frame=single]{python}
if age < 18:
    party = True
else:
    party = False
age += 1
        \end{minted}

\item Check type of a variable

        \begin{minted}[frame=single]{python}
type(age)
        \end{minted}
\item
  Repeat code as long as a given condition is met.

        \begin{minted}[frame=single]{python}
while boolean_condition:
    <code to repeat>
        \end{minted}

\item
  Repeat code over a given set.


        \begin{minted}[frame=single]{python}
for variable in iterable:
    <code to repeat>
        \end{minted}
\end{itemize}

\end{document}
